\chapter{Conclusions and perspectives}\label{CHAPTER_Summary}
Using density functional theory-based molecular dynamics (DFTMD) simulations, we have analyzed the interfacial structure and dynamics of electrolyte solutions containing alkali nitrates and alkali halides,
which share some similarities in terms of surface propensity.
In particular we have presented a detailed analysis of the vibrational sum-frequency generation (VSFG) spectra, hydrogen bond (HB) dynamics, and reorientation dynamics of water molecules at the solution/vapor interfaces. 
We have also provided a molecular interpretation of the interface vibrational spectra. 


We have shown that the use of simple models, such as small clusters are not suitable to reproduce the experimental spectra 
and cannot provide a microscopic interpretation of the VSFG spectra. Realistic models of the interface are required to address the 
perturbation of ions on the water surface. 


As a first system we have analyzed the behaviour of a salty interface containing alkali nitrates.
Both measured and calculated VSFG spectra shows a reduced intensity of the lower frequency portion region, 
when compared to the water/vapor interface. 
This reduction is attributed to the H-bonds established between nitrate and the surrounding water molecules at the interface.
This effects is only related to the presence of nitrate at the water surface and is \emph{not} due to the alkali metal ions.
We have shown that although the \Li can reside relative close to the water surface, also forming a water mediated
ion pair with \nit, its effect on the VSFG spectrum is not visible. The water molecule which mediate the interaction 
between nitrate and the alkali metal ions would produce a red-shifted peak in small water cluster's VDOS, but its influence is not visible 
in the VSFG spectra. Our simulations permit to describe the distribution of ions relative to the interface: 
nitrate ions are located in the uppermost layer of the interface, and alkali metal ions are located in the layer below 
and form with the anion a water separated ion pair.
The higher stability of the water-separated ion configuration is also proved by our calculation of the free energy difference between the different configurations. 

Using the instantaneous interface layer, we discussed
the thickness of the water/vapor interface, the relaxation time of the interfacial H-bonds, 
and the distribution of free OH bonds, which have an important contribution to the VSFG spectrum.
These properties all converge when the interface thickness is about 4 \AA. 
In particular, the distribution of the number of H-bonds per OH group is consistent with the frequency shift of the H-bonded OH stretching band of the VSFG spectrum. 
These results suggest that considering instantaneous interfaces is essential for understanding the microscopic structure about aqueous interfaces.

%For bulk system, based on the Luzar-Chandler HB population operator, 
%we calculated the correlation functions \CHB, $n(t)$, and $k(t)$, and obtained the rate constants ($k$ and $k'$) with the HB formation and breakage, 
%and then obtained the information about the HB lifetime.
To obtain information on the HB lifetime and its rate of breaking and forming, we have used the Luzar-Chandler HB population operator and calculated the correlation functions \CHB, $n(t)$, and $k(t)$ for bulk water. 
We find that both \nitrate--water and \I--water bonds have shorter lifetime than water--water bonds.
The HB relaxation and the lifetime of H-bonds
at the interface are dominated by the concentration of ions accumulated at the interface. 
Another general conclusion is that the HB strength between water molecules in the ions' second solvation shell is independent 
of the ion--water interactions in ions' first solvation shell.

We have shown that,
the method of interfacial molecule sampling (IMS) can give information on the HB breaking and reforming
rates at the water/vapor interface and permits to determine how far from the surface the interface affects the dynamics of H-bonds in water. 
Due to the movement of water molecules at the interface and in the bulk phase, the number of molecules at the interface will fluctuate.
Therefore, this method \emph{underestimates} the HB breaking rate constant of the water/vapor interface. 
We have provided a method based on the {instantaneous} surface and the new-defined
interfacial hydrogen bond (IHB) operator to obtain the interfacial HB dynamics of instantaneous water/vapor interfaces, and the thickness of the interface.  
The IHB method avoids sampling the molecules reside in the interfacial layer and
it also provide partial information on the HB breaking and reforming rates at the interface. 
Because of the definition of the IHB population, the IHB method \emph{overestimates} the HB breaking rate constant. 
The results for the two methods indicate that,
as the thickness of the water layer increases,
the HB breaking and reforming rate constants in the water layer {below} the instantaneous surface tends to be uniform. 
The real HB dynamical characteristics at the water/vapor interface 
are derived from the two extreme cases using the convergence behavior of the HB reaction rate constants and relaxation time 
of HB population correlation functions. 
Therefore, the result has given an estimate of the thickness of the water/vapor interface.  
The combination of the IMS method and the IHB population operator is extended to the solution/vapor interface. 
Due to the specific ions distribution in the normal direction of the interface,
the thickness of the solution/vapor interface is greater than the thickness of the water/vapor interface. 


In the last part of the thesis, the concept of instantaneous interface has been extended to analyze the first solvation shell around the ions.
For the alkali iodide solution/vapor interfaces, we found 
that the cations does not alter the H-bonding network outside the first hydration shell. 
It is concluded that no long-range structural-changing effects for alkali metal cations.
Moreover, the solvation shell HB method shows that, 
as far as the \Li, \Na, \K, NO$^-_3$ and \I ions are concerned, 
the HB dynamics for water molecule pairs does not vary significantly with these ions.


To sum up, from the results of nonlinear susceptibilities, which show bonded OH-stretching peaks with higher frequencies, 
we conclude that the water molecules at the interfaces of the alkali iodide solutions are participating 
in weaker H-bonds, compared with those at the water/vapor interface. 
The origin of these features can be found in the distribution of \I and the alkali metal cations
over the thickness on the order of 5 \A. 
%The same for alkali nitrate solution. 
Therefore, both the VSFG spectra of alkali nitrate and iodide solutions can be explained in the same way, 
in that the anions has propensity for the surface, and the weaker anion--H bonds at the topmost interface layer contribute to the blue-shifted H-bond band,
and the relative less free OH bonds produce a lower free OH stretching band.
This conclusion is verified by the distribution $P(n)$ of the number of H-bonds owned by a OH group at the instantaneous interface layer. 
By calculating the rotational anisotropy decay for water molecules at the instantaneous interface, 
we obtain that the average density of free OH bonds is an important factor that affect the decay rate of the reorientation relaxation of water molecules.


Some of the methods discussed in this thesis can be extended to other systems.
In particular, the combination of IHB and IMS can provide a basis for determining the thickness of the interface layer in other systems or environments, 
for example, to study the dynamics of water molecules around proteins. 
In recent years, there is a lot of experimental and simulation progress, for example, the diffusion acceleration effect on the glass surface\cite{ZhuL11,ZhangWei16}, 
and the aging effect of the non-equilibrium dynamics of the protein molecules on cell surface\cite{HuXiaohu16}. 
To describe these effects quantitatively, it is important to define the size of the interface accurately. 
We believe that combining the VSFG method, IHB and IMS methods will help us more accurately identify the range and size of the interface in these systems.
This will likely promote our understanding of the nature of these effects at interfaces.


Finally, as shown in this thesis, \abinitio simulations permit to widen our understanding of interface properties and the interactions between atoms.
However, the high computational cost prevents applications of AIMD calculations to larger systems.
One possible solution to this problem is to using the \abinitio data accumulated for small systems to train potentials (e.g. with machine learning approaches\cite{Norvig2010}), 
and then use these potentials to investigate larger systems such as more extended interfaces, 
e.g., at different ions concentrations\cite{Behler2007,Behler2011,Behler2014,Kolb2017}.
