\chapter{Summary}\label{CHAPTER_Summary}
Using DFTMD simulations, we have analyzed the interfacial structure and dynamics of electrolyte solutions containing alkali nitrates.
In particular we have presented a detailed analysis of the HB dynamics, reorientation dynamics of water molecules at the interface 
and we have calculated the interface vibrational spectra in order to provide a molecular interpretation of available experimental data. 
In view of the similarity between iodide ion and nitrate ion in the Hofmeister sequence, 
we also did the same calculation for the electrolyte solutions of alkali metal iodide. 
It is expected that a general understanding of the dynamical properties in solutions containing larger anions such as 
nitrate and iodide will be obtained.
%鉴于碘离子与硝酸根离子在Hofmeister序列中的相似性，我们有时也对碘化碱金属盐的溶液或其界面系统做了计算。以期望对含有硝酸根和碘离子等较大的阴离子的溶液中动力学性质得到一般的认识。

As a first system we have analyzed the behaviour of a salty interface containing LiNO$_3$.
Both the measured and calculated VSFG spectra shows a reduced intensity of the lower frequency portion region, 
when compared to the water/vapor interface. 
This reduction is attributed to the H-bonds established between the \nitrate and the surrounding water molecules at the interface.
This effects is only related to the presence of \nitrate at the water surface and is not affected by the presence of alkali metal ions.
Indeed we have shown that although the \Li can reside relative close to the water surface, also forming a water mediated
ion pair with \nit, its effect on the VSFG spectrum is not visible. The water molecule which mediate the interaction 
between the \nitrate and the \Li would produce a red-shifted peak in small water cluster, but its influence is not visible 
neither in the VSFG spectra. To verify this conclusion, the free energy of different configurations was calculated for 
larger water clusters in CP2K by the Blue-Moon method. The results still give consistent results: Li$^+$--NO$_3^-$ ion pairs 
separated by a water molecule have lower free energy than the configuration in which Li$^+$ is in direct contact with NO$_3^-$. 

We have also shown that the use of simple models, such as small cluster is not suitable to reproduce the experimental spectra 
and cannot provide a microscopic interpretation of the VSFG spectra. Realistic models of the interface are required to address the 
perturbation of the ion on the water surface. The elucidated mechanism is possibly more general to anions which have high 
propensity for the water surface, as for example other molecular ions.


From the results of nonlinear susceptibilities, which shows bonded OH-stretching peaks with higher frequencies, 
we conclude that the water molecules at the interfaces of LiI, NaI, and KI solutions are participating 
in weaker H-bonds, compared with those at the water/vapor interface. 
This conclusion is based on the DFTMD simulations, and % (with a simulation box with a length scale $\sim$ 10\A)
the origin of the characteristics come from a unique distribution of \I ions and alkali metal cations, 
which form a double layer \cite{Shultz2010} over the thickness on the order of 5--10 \A\ (see Appendix \ref{thickness_interface}).

For the bulk system, based on the Luzar-Chandler HB population operator, 
we calculated the correlation functions \CHB, $n(t)$, and $k(t)$, and obtained the reaction rate constants with the HB formation and breakage, 
and then obtained the information about the HB lifetime. 
%In order to analyze the HB dynamics on the interface, 
%we propose a statistical method which is based on the instantanous interface HB population operator for the instantaneous interface.
%Compared with traditional statistical methods, it is easier to implement and more efficient, 
%because it does not need to consider which molecules are within the instantaneous interface, 
%so there is no need to select the molecules on the interface and calculate the statistical average of physical quantities. 
%We took pure water interface and LiNO$_3$ solution as examples, and applied the above method to analyze the HB kinetics and HB lifetime on the interface. 
%This set of methods can be easily applied to general interface systems or solutions.
As we did in paragraph \ref{PARAGRAPH_LINO3} and \ref{PARAGRAPH_I--W}, we studied the population operators of nitrate ion--water hydrogen bond 
and iodide ion--water hydrogen bond and their correlation functions. In general solutions, water--water H-bonds can be extended to ion--water H-bonds, 
and then similar analysis can be done to study the HB dynamics.

Based on the DFMD simulations, the MS method % (i.e., select the water molecules in a certain thickness under the interface according to the molecular label)
can \emph{partially} gives information on the HB breaking and reforming reaction
rates through the water/vapor interface and therefore partially shows how much the interface affects the dynamics of H-bonds in water. 
This method \emph{underestimates} the HB breaking rate constant of the water/vapor interface. 
We have provided a method based on the instantaneous interface and the new-defined
IHB population operator to obtain the interfacial HB dynamics of instantaneous water/vapor interfaces.  
Using the correlation functions based on IHB population operator, we directly calculated the HB dynamics of water layer with a certain thickness 
under the instantaneous surface. 
The IHB method allows us to avoid choosing which molecules are located in the interfacial layer and
it also can provides partial information on the HB breaking and reforming reaction rates at the interface. 
However, it \emph{overestimates} the HB breaking rate constant. The calculation results in these two extreme cases
indicate that the HB breaking and reforming rate constants in the water layer \emph{below} the surface tends to be uniform 
(see Fig.\ref{fig:128w_itp_pure_water_pair_k_k_prime_ihb_both_schemes} a) 
as the thickness of the water layer increases. Therefore, the real HB dynamical characteristics in the air-water interface 
are derived from the two extreme cases. 
In particular, the result gives an estimate of the thickness ($\sim$ 3 \AA) of the water/vapor interface.

The combination of MS and IHB methods is also naturally extended to the solution interface. 
It has been confirmed that different ions in the electrolyte solution interface have their own unique distributions in the normal direction of the interface. 
Therefore, the thickness of the solution will be greater than the thickness of the water/vapor interface. 
In addition, we also regard the solvation shell of an ion as an interface, 
and defined the SHB population operator, which is similar to the IHB population.

The difference between the HB dynamics for H-bonds outside the first shell of the \Li and for nitrate-water H-bonds 
at the interface is not visible from the values of the HB relaxation time. They reflect the difference between HB dynamics in 
bulk water and at the water/vapor interface. For the interface of alkaline iodine solutions, we find 
that the cations does not alter the H-bonding network outside the first hydration shell. 
It is concluded that no long-range structural-changing effects for alkali metal cations.
Moreover, we use the SHB method to calculate the HB dynamics for the water molecules outside the first solvation shell.
As far as the types of ions (\Li, \Na, \K, NO$^-_3$ and \I ions) are concerned, 
the HB dynamics for water molecule pairs does not vary significantly with the type of ions.
%我们用SHB方法计算了离子第一溶解壳外的水分子的HBD.　结果显示，我我们所涉及到的离子种类，锂，钠，钾离子，硝酸根离子，碘离子，而言，球内的水分子与水分子之间的氢键动力学并不随着离子种类的不同而有明显差别。


Finally, by calculating the rotational anisotropy decay, we obtain non-single-exponential dynamics 
for the rotation of water molecules both at the surface and in bulk phase for alkaline 
iodine solutions. Therefore, the rotational motion of water molecules are not simply characterized by well-defined rate constants. 
Faster rotational anisotropy decay exists for water molecules at the interface of aqueous alkali-iodine solutions, 
which is the result of a different HB types (D$'$AA) from the usual HB type (DDAA) in bulk water. 
This effect on anisotropy decay is due to the H--I bond at the interface. Since the iodide's surface propensity is high, 
this difference of HB structure from the water/vapor interface changed the Im$\chi^{(2),\text{R}}$ spectrum and the HB dynamics 
of the interface of alkali-iodine solution. 

%\paragraph{Delocalization Effect in Hydrogen Bonds}
%The answer of the nature of H-bonds may lie with the electrons in the H-bonds. 
%Like all objects in nature, the electrons minimize their total energy, which includes their kinetic energy. 
%A reduced kinetic energy means a reduced momentum. According to the Heisenberg uncertainty principle, 
%the "delocalization" effect may occur for electrons in H-bonds, like in many other situations at sufficiently 
%low temperatures.\cite{Isaacs1999}

%(https://swift.cmbi.umcn.nl/teach/B2/HTML/hbonds.html)
%\paragraph{Discussion} We use DFT based molecular dynamics simulations to model alkali nitrate and alkaline iodine solutions, and calculate the SFG spectra, HB dynamics and 
%anisotropy decay of water molecules of these interfaces. The effects of alkali cations, 
%nitrate anions, and different bonding environments on these properties.

%The DFT calculations (despite taking electronic correlation into account) are not expensive,their cost is comparable with that of the Hartree–Fock method. Therefore, the same computer power allows us to explore much larger molecules than with other post-Hartree–Fock
%(correlation) methods.\cite{Piela07}

%DFT transforms the many-body problem of interacting
%electrons and nuclei into a coupled set of one-particle equations, which are
%computationally much more manageable.\cite{RMN02} 
%First-principles calculations based on the KS scheme of DFT have successfully predicted and explained a wide range of solid-state properties. However, it is true only for cohesive and structural properties. Systematicaly constructing functionals that are universally applicable is still a hard problem.
%Some examples of the failures of DFT are as follows.
%The band gaps of materials\cite{ASeidl}, the barriers of chemical reactions, 
%the energies of dissociating molecular ions, and charge transfer excitation energies are underestimated\cite{Kuehne12}. 
%The binding energies of charge transfer complexes and the response to an electric field in molecules and materials are overestimated. 
%Actually, all of these diverse issues are induced by the delocalization error of approximate functionals, due to the dominating Coulomb term that pushes electrons apart.\cite{Cohen08,Sanchez08,Cohen08b} 
%Furthermore, typical DFT calculations fail to describe degenerate or near-degenerate states, such as arise in transition metal systems, the breaking of chemical bonds, and strongly correlated materials. These problems come from another error--the static correlation error of approximate functionals, because it is difficult to describe the interaction of degenerate states by using the electron density.

%The delocalization error and static correlation error of commonly used approximations \cite{Cohen08} can be understood through the perspective of fractional charges and fractional spins and reducing these errors will provide wider applications of DFT.
